Price of Anarchy for Mean Field Games

### 2018-09-28 PoA.tex
new templete

\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage[toc,page]{appendix}

@@

\title{Price of Anarchy for Mean Field Games}
\author{
Ren\'{e} Carmona\thanks{Operations Research and Financial Engineering, Princeton University, Partially supported by NSF \#DMS-1716673 and ARO \#W911NF-17-1-0578} 
\and 
Christy V. Graves\thanks{Program in Applied and Computational Mathematics, Princeton University, Partially supported by NSF \#DMS-1515753 and NSF GRFP}
\and
Zongjun Tan \thanks{Operations Research and Financial Engineering, Princeton University, Partially supported by NSF \#DMS-1515753} 
}

@@

>>>>

\documentclass[proc]{edpsmath}
\usepackage{fullpage}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage[toc,page]{appendix}

@@

@@

\title{Price of Anarchy for Mean Field Games}

\author{Ren\'{e} Carmona} \address{Operations Research and Financial Engineering, Princeton University, Partially supported by NSF \#DMS-1716673 and ARO \#W911NF-17-1-0578}

\author{Christy V. Graves} \address{Program in Applied and Computational Mathematics, Princeton University, Partially supported by NSF \#DMS-1515753 and NSF GRFP}

\author{ Zongjun Tan} \address{Operations Research and Financial Engineering, Princeton University, Partially supported by NSF \#DMS-1515753}
